Whose voices are heard?

### 2024-01-08 paper/app-eventdata.qmd
major editing

Events were filtered from @ClarkMMPdata2019 to include only protests in the UK.
Most variables in the raw data were either enriched or recoded before the main analysis.

>>>>

To merge the two datasets, the data on protest reporting in the UK and protest event data from @ClarkMMPdata2019. I employed a two-staged strategy:
first, I selected all articles in the newspaper dataset that were published no earlier than seven days before an event started and no later than 30 days after it ended;
then I used the variables "Protest Locations", "Protest Group Identity" and "Protester Demands" to extract suitable keywords.
I then used keywords to filter the articles selected in the first stage:
articles were discarded if they did not feature at least one of the keywords.
This selection was manually validated and overlaps between events were separated by hand.
Overall, 5,639 articles could be matched with the 471 events from the database.

The list of events was obtained by filtering MMP data from @ClarkMMPdata2019 to include only protests in the UK.
Most variables in the raw data were either enriched or recoded before the main analysis.
